Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-15 proposal/proposal.tex
Added Base Station Section
Added Abstract

\begin{abstract}
300 words or less. Talk about the motivation behind this project. Why it is important.
\end{abstract}

@@

@@

\bibitem{raspbian} \emph{Raspbian} [Online] Available: \url{http://www.raspbian.org/}
\end{thebibliography}

>>>>

\begin{abstract}
This proposal describes a parking lot monitoring system to be used at the Colorado School of Mines (CSM). The system will help campus members enjoy a better parking experience by spending less time trying to find open lots. This is a semester project for the Computer Science graduate course \emph{Wireless Sensor Networks}, taught by Dr. Tracy Camp at CSM. The proposed work will be an extension of a project started by campus computing group ACMx, which uses a wireless sensor network to track the number of cars in specific parking lots. The system will extend the ACMx project by adding components to the sensor network that record the license plate numbers of cars as they enter and exit lots. The information gathered by the sensor network will be displayed on a website that will allow users to survey the state of the lots before arriving, allowing them to make informed parking decisions. The website will also be the result of collaboration between the authors of this proposal and the ACMx group. The proposal provides some background information, describes the proposed system and its components, and discusses implementation strategies. The goal of the project is a real-world deployment on the CSM campus by May 2014.
\end{abstract}

@@

\bibitem{raspbian} \emph{Raspbian} [Online] Available: \url{http://www.raspbian.org/}

@@

\end{thebibliography}
